### 2023-01-12 code/plots.Rmd
PPO has learned Reed '79

```{r}
## reticulate::source_python("msy.py")
```

```{r}
escapement <- read_csv("../data/escapement.csv")
escapement |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
```

>>>>

```{r}
ppo <- read_csv("../data/PPO.csv")
```

```{r}
ppo |> 
  mutate(pop = (sp1+1)/2, 
         escapement = pop - action * pop) |> 
  ggplot(aes(t, escapement, group=rep)) + geom_line() + ylim(0,1)
```

```{r}
msy <- read_csv("../data/msy.csv")
best <- msy |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best
```
```{r}
msy_sim <- msy |>
  filter(action == best$action) |> 
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")

msy_sim |>
  ggplot(aes(t, abundance, group = interaction(species, rep), col=species)) + 
    geom_line(alpha=0.5)

```

```{r}
escapement <- read_csv("../data/escapement.csv.gz")
best_e <- escapement |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best_e
```

```{r}
esc_sims <- escapement |>
  filter(action == best_e$action) |> 
  mutate(effort = pmax(1 - action / sp1, 0)) |>
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")

esc_sims |>
  ggplot(aes(t, abundance, group = interaction(species, rep), col=species)) + geom_line(alpha=0.2)

esc_sims |> ggplot(aes(t,action, group=rep)) + geom_line(alpha=.2)

esc_sims |> ggplot(aes(t,effort, group=rep)) + geom_line(alpha=.2)
```
